Exploring mathematical objects from custom-tailored mathematical universes

### 2020-01-20 paper-filmat.tex
Pointers to introductory literature

@@

@@

Outline:

@@

* XXX Syntactical vs. semantical interpretation
* XXX phone call analogy
* XXX quick overview of the several aspects of toposes (maybe at the end, as an outlook?)
* XXX allowing a switch of perspective
* XXX applications in mathematical practice
* XXX int. logic as common denominator
* XXX arbitrariness of the "standard axioms"
* XXX importance of having an adapted language
* XXX Source https://plato.stanford.edu/entries/category-theory/ for relevant literature
* XXX the internal language as a generalized modal operator
* XXX use the phrase "very rich and very deep" (or similarly) about set theory
* XXX Sven(?)
* XXX Kripke models
* XXX more pointers to topos literature
* XXX Reference for the effective topos
* XXX A topos is more than its semantics
* XXX Reference: Moerdijk
* XXX Check references everywhere (give good pointers)
* XXX toposes are not small (Figure 1)
* XXX internal/external

@@

* XXX Mike
* XXX Hamkins multiverse

>>>>

We intend this contribution to be self-contained and do not assume familiarity with
topos theory or category theory. Readers who would like to learn more details
are directed to a gentle introduction to topos theory by Tom
Leinster~\cite{leinster:introduction}.
Standard references for the internal
language of toposes include~\cite[Chapter~VI]{moerdijk-maclane:sheaves-logic},
\cite[Chapter~14]{goldblatt:topoi},
\cite{caramello:preliminaries}, \cite{streicher:ctcl}, \cite{shulman:categorical-logic},
\cite[Chapter~6]{borceux:handbook3} and~\cite[Part~D]{johnstone:elephant}.

@@

Introductory literature on the \effective topos
includes~\cite{hyland:effective-topos,oosten:realizability,phoa:effective,bauer:c2c}.

@@

@@

* XXX Syntactical vs. semantical interpretation
* XXX phone call analogy
* XXX quick overview of the several aspects of toposes (maybe at the end, as an outlook?)
* XXX allowing a switch of perspective
* XXX applications in mathematical practice
* XXX int. logic as common denominator
* XXX arbitrariness of the "standard axioms"
* XXX importance of having an adapted language
* XXX Source https://plato.stanford.edu/entries/category-theory/ for relevant literature
* XXX the internal language as a generalized modal operator
* XXX use the phrase "very rich and very deep" (or similarly) about set theory
* XXX Sven(?)
* XXX Kripke models
* XXX more pointers to topos literature
* XXX A topos is more than its semantics
* XXX Check references everywhere (give good pointers)
* XXX toposes are not small (Figure 1)
* XXX internal/external

@@

* XXX Hamkins multiverse
